Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-05 cordillera-cycle.tex
Minor corrections in model setup.

The simulations presented here were run using Parallel Ice Sheet Model (PISM,
development version~11b0a7f), an open-source, finite-difference, shallow ice
sheet model \aref. The model takes basal topography, sea level, geothermal heat flux
and climate forcing, as input fields and computes the evolution of ice extent
and thickness in time, the thermal and dynamic state of the ice sheet, and
the associated lithospheric response. Our modelling domain encompasses the
entire area covered by the Cordilleran ice sheet at the last glacial maximum
(Fig.~\ref{fig:locmap}).

@@

Temperature offset time-series ${\Delta}T_{TS}$ are derived from proxy records from
the Greenland Ice Core Project (GRIP), the North Greenland Ice Core Project
(NGRIP), the European Project for Ice Coring in Antarctica (EPICA), the Lake
Vostok ice core, and Ocean Drilling Program (ODP) sites 1012 and 1020, both
located off the Californian shore. Palaeo-temperatures from the GRIP and NGRIP
records were calculated using a quadratic equation \aref:
\begin{equation}
    {\Delta}T_{TS}(t) = -11.88[\chem{\delta^{18}O(t)}-\chem{\delta^{18}O}(0)]
                        -0.1925[\chem{\delta^{18}O(t)}^2-\chem{\delta^{18}O}(0)^2]
\end{equation}
while the temperature reconstructions from the Antarctic and oceanic cores were
provided by their authors \aref. All records were scaled linearly in
order to simulate comparable ice volumes and realistic ice extents at the last
glacial maximum (Table~\ref{tab:records}, Fig.~\ref{fig:timeseries}).

@@

This correction accounts
for the evolution of ice thickness on the one hand, and differences between the
climate forcing reference topography and the ice flow model basal topography on
the other hand. An annual lapse rate of
$\gamma = 6\,\unit{{\degree}C\,km^{-1}}$
is used in all simulations.

>>>>

The simulations presented here were run using Parallel Ice Sheet Model (PISM,
development version~11b0a7f), an open-source, finite-difference, shallow ice
sheet model \aref. The model inputs basal topography, sea level, geothermal
heat flux and climate forcing, and computes the evolution of ice extent
and thickness in time, the thermal and dynamic state of the ice sheet, and
the associated lithospheric response. Our modelling domain encompasses the
entire area covered by the Cordilleran ice sheet at the last glacial maximum
(Fig.~\ref{fig:locmap}).

@@

Temperature offset time-series ${\Delta}T_{TS}$ are derived from proxy records from
the Greenland Ice Core Project (GRIP), the North Greenland Ice Core Project
(NGRIP), the European Project for Ice Coring in Antarctica (EPICA), the Lake
Vostok ice core, and Ocean Drilling Program (ODP) sites 1012 and 1020, both
located off the Californian shore. Palaeo-temperatures from the GRIP and NGRIP
records were calculated using a quadratic equation \aref:
\begin{equation}
    {\Delta}T_{TS}(t) = -11.88[\chem{\delta^{18}O(t)}-\chem{\delta^{18}O}(0)]
                        -0.1925[\chem{\delta^{18}O(t)}^2-\chem{\delta^{18}O}(0)^2]
\end{equation}
while the temperature reconstructions from the Antarctic and oceanic cores were
provided by their authors \aref. All records were scaled linearly in
order to simulate realistic and comparable ice extents at the last
glacial maximum (Table~\ref{tab:records}, Fig.~\ref{fig:timeseries}).

@@

This correction accounts for the evolution of ice thickness $h$ on the one
hand, and for differences between the climate forcing reference topography and
the ice flow model basal topography $z_{b}-z_{ref}$ on the other hand. An
annual lapse rate of $\gamma = 6\,\unit{{\degree}C\,km^{-1}}$ is used in all
simulations.
